Stemmer Tool Manual

### 2016-01-21 tex/Manual.tex
update with cmake and qt5 instructions

Sarf is an open source tool. The code is currently hosted on google code under the project name ``atmine''. To download the code, you can use the svn interface:\\
\begin{verbatim}
svn checkout http://atmine.googlecode.com/svn/trunk/ atmine-read-only.
\end{verbatim}
Preferablly, get a stable version of Sarf from the download section under:\\
\begin{verbatim}
http://code.google.com/p/atmine/downloads/list
\end{verbatim}
\paragraph{}
From the link above, download a zipped file named ``ATSarf-0.1.tar.bz2'' which contains all the files required to run the morphological analyzer along with all the applications implemented based on it. After downloading the compressed folder, extract it and you should have a folder named ``ATSarf-0.1''. Inside this folder, you'll find ``ATSarf''; the top folder of Sarf.\\
You also need the encoded lexicon in the zip file ``Bama-Public.zip''. This zip file is found in ``ATsarf-0.1'' introduced above or in ``ATSarf/bin'' directory if you are using svn to download the code. You have to extract this file in your running directory in order for the tool to work correctly.

@@

\subsection{Dependencies}
\label{subsec:dependencies}
In order to be able to build and run Sarf, the following dependencies must be installed:
\begin{itemize}
\item mysql-client
\item mysql-server
\item libmysqlcppconn4
\item libmysqlcppconn-dev
%\item libqjson-dev
%\item subversion
\item qt-sdk
%\item qtcreator
\item g++
%\item graphviz
\end{itemize}
The above tools can be downloaded and installed using the ``Synaptic Package Manager'' in ubuntu systems or through the ``apt-get'' command. You can use similar commands such as yum in other linux distributions.
\subsubsection{datrie}
You also need to download the double-array trie library called ``datrie''. Datrie can be downloaded from the following link:\\
\url{http://linux.thai.net/~thep/datrie/datrie.html#Download }\\
After downloading the trie structure to a destination you specify, go to {\bf datrie/libdatrie-0.2.3} and apply the following commands to configure and build.
\begin{enumerate}
\item ./configure
\item make
\end{enumerate}
Note that the name of the folder ``libdatrie-0.2.3'' includes the version of the library downloaded ``0.2.3''.If you download another version of this library, it will have a different name referring to a different version. Using any of the other versions of datrie shouldn't lead to anu problem, however it is preffered to use the same version as the one introduced above.

@@

\subsubsection{Qt link}
Moreover, you need to set a link to the Qt library as well using the same procedure used for the preceding link. 
The following command should do the trick if you are using an Ubuntu 10.10 version of linux:
\begin{verbatim}
ln -s /usr/share/qt4 qt
\end{verbatim}
Otherwis, you'll have to find the qt4 files on your system and create a link for them.

@@

\subsection{Build}
Now we are ready to build Sarf.
Go to the ``ATSarf/'' directory and build the tool using the following command:
\begin{verbatim}
make
\end{verbatim}

>>>>

Sarf is an open source tool. The code is currently hosted on google code under the project name ``atmine''. To download the code, you can use the svn interface:\\

\begin{verbatim}
git clone http://github.com/codelogicanalysis/atmine 
\end{verbatim}

%\begin{verbatim}
%svn checkout http://atmine.googlecode.com/svn/trunk/ atmine-read-only.
%\end{verbatim}
%Preferablly, get a stable version of Sarf from the download section under:\\
%\begin{verbatim}
%http://code.google.com/p/atmine/downloads/list
%\end{verbatim}

\paragraph{}
From the link above, download a zipped file named ``ATSarf-0.1.tar.bz2'' which contains all the files required to run the morphological analyzer along with all the applications implemented based on it. After downloading the compressed folder, extract it and you should have a folder named ``ATSarf-0.1''. Inside this folder, you'll find ``ATSarf''; the top folder of Sarf.\\
You also need the encoded lexicon in the zip file ``Bama-Public.zip''. This zip file is found in ``ATsarf-0.1'' introduced above or in ``ATSarf/bin'' directory if you are using svn to download the code. You have to extract this file in your running directory in order for the tool to work correctly.

@@

\subsection{Dependencies}
\label{subsec:dependencies}
In order to be able to build and run Sarf, the following dependencies must be installed:
\begin{itemize}
\item mysql-client
\item mysql-server
\item libmysqlcppconn4
\item libmysqlcppconn-dev
%\item libqjson-dev
%\item subversion
\item qt-sdk (Qt 5.2 minimum) 
%\item qtcreator
\item g++
%\item graphviz
\end{itemize}

The above tools can be downloaded and installed using the ``Synaptic Package Manager'' in ubuntu systems or through the ``apt-get'' command. You can use similar commands such as yum in other linux distributions.
\subsubsection{datrie}
You also need to download the double-array trie library called ``datrie''. Datrie can be downloaded from the following link:\\
\url{http://linux.thai.net/~thep/datrie/datrie.html#Download }\\
After downloading the trie structure to a destination you specify, go to {\bf datrie/libdatrie-0.2.3} and apply the following commands to configure and build.
\begin{enumerate}
\item ./configure
\item make
\end{enumerate}

Note that the name of the folder ``libdatrie-0.2.3'' includes the version of the library downloaded ``0.2.3''.If you download another version of this library, it will have a different name referring to a different version. Using any of the other versions of datrie shouldn't lead to anu problem, however it is preffered to use the same version as the one introduced above.

@@

\subsubsection{Qt link}
Moreover, you need to set a link to the Qt library as well using the same procedure used for the preceding link. 
The following command should do the trick if you are using an Ubuntu 10.10 version of linux:
\begin{verbatim}
ln -s /usr/share/qt5 qt
\end{verbatim}
Otherwis, you'll have to find the qt4 files on your system and create a link for them.

@@

\subsection{Build}
Now we are ready to build Sarf.
Go to the ``ATSarf/'' directory and build the tool using the following command:
\begin{verbatim}
%make
1. Checkout the source code
2. mkdir build
3. cd build
4. cmake ../atmine/ATSarf
5. make
\end{verbatim}
